The complex network of trophic interactions in a subAntarctic oceanic Marine Protected Area

### 2023-05-08 MS_ToSubmit/MS_Burdwood_foodweb.tex
2nd version w/ coauthors suggs

      \affiliation[1]{Centro Austral de Investigaciones Cientificas
(CADIC-CONICET), Argentina}
    \affiliation[2]{Instituto Antartico Argentino (IAA), Argentina}
    \affiliation[3]{Instituto de Ciencias Polares, Ambiente y Recursos
Naturales (ICPA), Universidad de Tierra del Fuego (UNTDF), Argentina}
    \affiliation[4]{Instituto de Investigaciones Marinas y Costeras
(IIMYC), Universidad Nacional de Mar del Plata-CONICET, Argentina}
    \affiliation[5]{Wildlife Conservation Society, Argentina}
    \affiliation[6]{Instituto de Biodiversidad y Biología Experimental y
Aplicada (IBBEA), Universidad de Buenos Aires-CONICET, Argentina}
    \affiliation[7]{Museo Argentino de Ciencias Naturales ``Bernardino
Rivadavia'', Argentina}
    \affiliation[8]{Instituto de Diversidad y Ecología Animal
(IDEA-CONICET)}
    \affiliation[9]{Facultad de Ciencias Exactas, Físicas y Naturales,
Universidad Nacional de Córdoba (UNC), Argentina}
    \cortext[cor1]{Corresponding author}

  \begin{abstract}
  Globally, the total area of the world ocean designated under marine
  protection has increased in the recent decades. The majority of these
  Marine Protected Areas (MPAs) focus on the presence of particularly
  vulnerable, keystone, or charismatic species, large numbers of endemic
  species, and/or high biodiversity across taxonomic levels. In the
  sub-Antarctic region, the level of ocean protection is mainly
  associated to oceanic islands, except for the MPAs Namuncurá - Banco
  Burdwood I and II (MPA N-BB, 53º--55ºS and 56º--62ºW, respectively),
  which are associated to a submarine plateau and its southern adjacent
  deep slope region, respectively. Here, we present the first detailed
  analysis of the network of predator-prey interactions (food web) for
  the MPA N-BB ecosystem. We applied a network approach to characterize
  the food web in terms of complexity and structure, and identifying the
  species' role in such a framework. In terms of complexity, the MPA
  N-BB food web consisted of 1778 predator-prey interactions and 379
  species, with a link density of 4.69 and a connectance of 0.01. In
  terms of structure, almost half of the consumers were omnivores
  (0.48), and the network displayed a small-world pattern. These
  findings suggest that the ecosystem might be vulnerable to external
  perturbations targeting highly connected species, although structural
  properties might provide resilience and resistance, resulting in a
  rearranged structure that preserves its original functions.
  Furthermore, we identified several species as important in terms of
  different aspects of trophic structure and functioning, and response
  to perturbations. We suggest that generalist species, mainly fishes,
  play a crucial role in the ecosystem's bentho-pelagic coupling
  process. In addition, we propose that other species besides the
  longtail southern cod \emph{Patagonotothen ramsayi} and the Fueguian
  sprat \emph{Sprattus fuegensis} should be considered as relevant
  energy transfers for the ecosystem. Finally, we argue that the
  diversity of species, including both the benthic and pelagic habitats,
  is responsible for seccuring the connectivity within the food web
  against perturbations, therefore contributing to the structure and
  stability of the ecosystem.
  \end{abstract}
    \begin{keyword}
    Food web \sep Complexity \sep Structure \sep Marine Protected
Area \sep 
    Southwest Atlantic
  \end{keyword}

@@

High-latitude marine ecosystems, such as the MPA N-BB, are considered
complex systems in terms of biodiversity and ecological interactions
(Cordone et al., 2020; Day et al., 2013; Kortsch et al., 2019; Trathan
et al., 2021). Although there is a robust knowledge about the complexity
considering the richness of the benthic and plankton communities in the
MPA N-BB ecosystem (APN, 2022; Guinder et al., 2020; Schejter et al.,
2016, 2020), a better understanding of species interactions' complexity
and structure is needed. This aspect can be tackled by analyzing one of
the most frequent relationships between species: the predator-prey
interaction (Bascompte, 2009). The sum of predator-prey or trophic
interactions of a particular region is referred to as a food web,
representing the roadmap for matter and energy flow in an ecosystem. In
recent years, network approaches have been successfully applied to study
complex high-latitude marine ecosystems, improving our knowledge on
structure, functioning, and response to environmental/anthropogenic
changes (Cordone et al., 2018; Funes et al., 2022; Kortsch et al., 2015;
Marina et al., 2023). Among anthropogenic threats, it is worth
mentioning that contaminants like mercury and microplastics have been
recently reported as important threats to the MPA N-BB region (Cossi et
al., 2021; Di Mauro et al., 2022; Fioramonti et al., 2022).

In the present work, we present the first detailed analysis of the
network of predator-prey interactions, hereafter food web, for the MPA
N-BB ecosystem. For this, we applied a network approach to a highly
resolved food web. The objective was twofold: characterize the food web
in terms of complexity and structure, and identify the species' role in
such a network framework.

@@

We analyzed the MPA N-BB network of trophic interactions, or food web,
at two levels: A) network, considering species and interactions of the
whole network; and B) species, considering interactions and species
related to a particular species (Table 1).

The network-level analysis aims to characterize the food web in terms of
complexity and structure. For this, we calculated several network
properties commonly used to describe empirical food webs (Pascual \&
Dunne, 2005): (1) number of species S; (2) number of interactions or
links L; (3) link density L/S; (4) connectance L/S\^{}2; (5) omnivory
Omn; and (6) small-world pattern. In order to explore the small-world
phenomenon, we analyzed the characteristic path length (CPL) and the
clustering coefficient (CC). The CPL is the average shortest path length
between all pairs of nodes (Watts \& Strogatz, 1998). Here, CPL was
calculated as the average number of nodes in the shortest path
\(CPL_{Min} (i,j)\) between all pairs of nodes \(S(i,j)\) in a network
averaged over \(S(S-1)/2\) nodes:

@@

In terms of complexity, the MPA Namuncurá - Banco Burdwood food web
(N-BB I and II) consisted of 1778 predator-prey interactions and 379
species, where 93\% of them were defined at the species taxonomical
level (Figure 2, Table S2). The food web presented a link density (e.g.,
the average number of interactions per species) of 4.69, and a
connectance of 0.01. Almost half of the consumers were omnivores (0.48),
feeding on sources at different trophic levels. The food web displayed a
small-world pattern, meaning that the path length was lower and the
clustering coefficient higher than the random networks (Table 2).

@@

\caption{\label{tab:table2}Network-level properties of the MPA Namuncurá - Banco Burdwood food web. CPL: Characteristic Path Length; CC: Clustering Coefficient; SW: Small-World pattern. See table 1 for definitions and ecological relevance.}
\centering
\begin{tabular}[t]{r|r|r|r|r|r|r|l}
\hline
\textbf{Species} & \textbf{Interactions} & \textbf{Density} & \textbf{Connectance} & \textbf{Omnivory} & \textbf{CPL} & \textbf{CC} & \textbf{SW}\\
\hline
380 & 1785 & 4.7 & 0.01 & 0.48 & 2.99 & 0.08 & True\\
\hline
\end{tabular}
\end{table}

The degree distribution of the food web showed an asymmetric frequency
in the number of interactions, where most of the species had a
relatively low number of interactions and few species concentrated most
of them (Figure 3A). The distribution of prey among predators showed
that most consumers fed on a low number of prey whereas few had multiple
preys (Figure 3B). The top-five predators in number of prey were:
yellowfin notothen \emph{Patagonotothen guntheri} (Notothenioid fish, 52
prey), rock cod \emph{Patagonotothen ramsayi} (Notothenioid fish, 50
prey), Patagonian toothfish \emph{Dissostichus eleginoides}
(Notothenioid fish, 30 prey), broad nose skate \emph{Bathyraja
brachyurops} (Chondrichthyan, 30 prey), and graytail skate
\emph{Bathyraja griseocauda} (Chondrichthyan, 28 prey). Following the
same distribution pattern, few prey presented multiple predators (Figure
3C). The top-five prey in number of predators were: Detritus
(Non-living, 153 predators), the three categories of Diatoms considered
(benthic, centric and pennate, 72 predators on average), and species of
the genus \emph{Euphausia} (Zooplankton, 46 predators). Finally, taking
into account the interactions within each functional group, most
interactions were concentrated in a few species (Figure 3D). The most
evident species were: \emph{Themisto gaudichaudii} (Amphipoda),
\emph{Zygochlamys patagonica} (Bivalvia), \emph{Aspidostoma giganteum}
(Bryozoa), \emph{Munida gregaria} (Decapoda), \emph{Patagonotothen
ramsayi} and \emph{Patagonotothen guntheri} (bentho-pelagic fish),
\emph{Psychrolutes marmoratus} (demersal fish), and species of
\emph{Euphausia} (Zooplankton). Overall, there is an evident asymmetry
in the distribution of interactions among species at different levels in
the MPA N-BB food web.

@@

\caption{Degree distributions for the (A) food web, for (B) prey among predators, (C) predators among prey, and (D) for each functional group. Groups are vertically ordered by increasing trophic level; groups with less than 3 species were not plotted (e.g., pelagic fish).}\label{fig:figure3}
\end{figure}

@@

Most species in the food web were consumers, 336 out of 379; the rest
were primary producers, such as diatoms (phytoplankton), and non-living
food sources like detritus and necromass.

We found different relationships between the species trophic level (TL)
and the rest of the analysed species-level properties (Figure 4A-D). The
most evident significant relationship was with trophic similarity,
i.e.~the higher the species' TL, the lower the trophic similarity or the
higher the uniqueness in terms of trophic role (Figure 4C). Here it is
noteworthy to highlight those high-trophic level species with low values
of trophic similarity: \emph{Bathyraja macloviana} and \emph{Squalus
acanthias} (Chondrichthyans), \emph{Diplopteraster clarki} and
\emph{Pteraster sp} (echinoderms), \emph{Phalacrocorax atriceps} and
\emph{Eudyptes chrysocome} (sea birds), and \emph{Lagenorhynchus
cruciger} and \emph{Mesoplodon bowdoini} (marine mammals) (Table S3).

We also found a significant negative relationship between TL and
closeness, however less evident, meaning that low-TL species are
relatively closer to any other species in the food web (Figure 4B).
Species of genera \emph{Calanus} and \emph{Euphausia}, and species of
Brachiopoda, all with TL \textless{} 3, registered the highest closeness
values (Table S3).

Notably, species of mid-TLs (3-4) showed the highest values of
betweenness, meaning that those species participated in the highest
number of shortest paths between species (Figure 4A). The following are
the species with the highest values: \emph{Patagonotothen ramsayi},
\emph{Dissostichus eleginoides}, \emph{Salilota australis} (fishes),
\emph{Doryteuthis gahi} (Cephalopoda), and \emph{Patagonotothen
guntheri} (Notothenioid fish) (Table S3).

Considering the topological role, `module specialist' species were the
most frequent and presented a wide TL range (1 - 4.77); `module hub' was
constrained to mid-TL species (2.48 - 3.92); `module connector' from low
to mid-TLs (1 - 3.86); and `network connector', the least frequent, had
all of its species in TL = 1, except for one with TL = 3.47 (Figure 4D,
see Figure S2 for species' topological roles in a food web graph
framework). Here it is important to highlight the two latter topological
roles because they are responsible for linking modules and maintaining
the connectivity of the food web: 40 species (5 network connectors + 35
module connectors) from 20 different functional groups with a TL range =
1 - 3.86. The following were the five species with a network connector
role: Detritus, Diatoms (benthic, centric and pennate), and
\emph{Patagonotothen ramsayi}. The 35 species with a module connector
role represent these functional groups: Amphipoda, Bivalvia,
Brachiopoda, Bryozoa, Cnidaria, Cumacea, Decapoda, detritus, Diatoms,
Dinoflagellates, Echinodermata, fish (bentho-pelagic and demersal
Osteichthyes, and Chondrychthyes), Foraminifera, Polychaeta, Porifera,
Pycnogonida, sea birds, and zooplankton (see Supplementary Material
Table S3 for the identity of the species).

@@

\caption{Species-level properties by trophic level: (A) betweenness, (B) closeness, (C) trophic similarity, and (D) topological role. Each point represents a species. Linear regressions for betweenness ($y = x - , R^2 = , p-value < $), closeness ($y = x - , R^2 = , p-value = $) and trophic similarity ($y = x - , R^2 = , p-value = $). Note that for panels A, B and C only species with TLs equal or greater than 2 were considered.}\label{fig:figure4}
\end{figure}

@@

It is suggested that the small-world pattern, i.e., a network with short
path length and high clustering coefficient, is not frequent in complex
marine food webs, mainly due to a low clustering coefficient compared to
random networks (Dunne et al., 2002c; Marina, Saravia, et al., 2018).
However, the food web of the MPA N-BB does display a small-world
pattern. Consequences of this could be of great importance in
recognizing evolutionary paths and the vulnerability to perturbations
(Montoya \& Solé, 2002). On the one hand, a short path length implies a
rapid spread of an impact (e.g., contaminant, population fluctuation,
local extinction) throughout the network and, at the same time, more
potentially adaptive dynamics in the face of external perturbations
(Montoya \& Solé, 2002; Williams et al., 2002). On the other hand, a
high clustering coefficient indicates the formation of subnetworks
composed only by the neighbours of particular species. This translates
into a greater resistance of the network due to the confinement of
perturbations mainly within subnetworks and not spreading between them
(Heer et al., 2020; Kortsch et al., 2019). Overall, a small-world
topology provides ecological networks with greater resilience and
resistance (Bornatowski et al., 2017; Dormann et al., 2017).

@@

We have identified that most of the consumers in the food web of the MPA
N-BB either has a narrow diet or are specialists, while few present a
broad diet. The most evident generalist species are \emph{Patagonotothen
guntheri} (Covatti Ale et al., 2022), \emph{P. ramsayi} (Fischer et al.,
2022), \emph{Dissostichus eleginoides} (Troccoli et al., 2020),
\emph{Bathyraja brachyurops} (Belleggia et al., 2008), and \emph{B.
griseocauda} (Bellegia et al., 2014), with more than 25 potential prey.
Since these species present mid-trophic positions in the food web (3-4),
acting as predator and prey, they might be important links between lower
and higher trophic levels. This result is in agreement with the sole
analysis, using stable isotopes, that exists so far for the trophic
structure of the MPA N-BB (Riccialdelli et al., 2020), and resembles
other high-latitude marine systems of the Southwest Atlantic and
Antarctic regions (Arkhipkin \& Laptikhovsky, 2013; Marina, Salinas, et
al., 2018). The importance of these particular generalist species also
arises since they feed on the benthic and pelagic habitats (Covatti Ale
et al., 2022; Fischer et al., 2022; Troccoli et al., 2020), linking
these realms and contributing to the vertical carbon flow.

On the other hand, a low number of prey are consumed by many predators
in the food web of the MPA N-BB. This suggests that there are dominant
food sources from which most consumers depend on and from where the
ecosystem energy is being transferred to the upper trophic levels. The
most demanded source we identified in this study (i.e.~detritus)
supports the abundant benthic community of filter-feeders (Schejter et
al., 2016). Furthermore, we found that the second and third-most
consumed prey were diatoms and species of \emph{Euphausia},
respectively, which are essential sources for the diverse zooplankton
community (Spinelli et al., 2020), mid-TL consumers like the Fuegian
sprat \emph{Sprattus fuegensis} (Padovani et al., 2021) and
\emph{Patagonotothen ramsayi} (Fischer et al., 2022), and top predators
(Raya Rey, 2022; Riccialdelli, 2022).

@@

Ecosystems with a pronounced `wasp-waist' structure are suggested to
present a high trophic redundancy, since many species would show similar
trophic habits (Cury et al., 2000). The significant negative
relationship between trophic similarity and trophic level enhances the
hypothesis of functional similarity at low and mid-TL species compared
to higher TL species for the MPA N-BB food web (Riccialdelli et al.,
2020). At the same time, our results highlight the uniqueness in terms
of the trophic role of high-TL predators. Here, not only the expected
pelagic animals such as marine mammals and sea birds arise as relevant,
but also benthic vertebrate (chondrichthyans \emph{Bathyraja macloviana}
and \emph{Squalus acanthias}) and invertebrate species (echinoderms
\emph{Diplopteraster clarki} and \emph{Pteraster sp}) are noteworthy.
The role that such species play in the MPA N-BB ecosystem is unique and
perturbations on them might result in unprecedented changes at the
trophic structure and functioning level.

@@

The food web studied in the present work might be more representative of
the MPA Namuncurá - Banco Burdwood I ecosystem, which comprises the
shallow submarine plateau called Burdwood Bank. This is related to the
sampling effort that was conducted during the research cruises in the
former MPA compared to the MPA N-BB II (i.e.~deep flanks to the south).
As a consequence most of the data we used to build the network come from
studies performed in the MPA N-BB I. Despite this fact, we decided to
build the food web considering both MPAs due to the tight oceanographic
and ecological connection that exists among them (references in APN,
2022).

@@

The MPA N-BB I presents complex oceanographic conditions that generate
an internal spatial heterogeneity, mainly along its longitudinal axis
(Matano et al., 2019). Up to date this heterogeneity has been reflected
in phytoplankton and zooplankton communities (Bértola et al., 2018;
García Alonso et al., 2020; Spinelli et al., 2020), and in fish
assemblages (Delpiani et al., 2020). Moreover, seasonal variations also
occur in some physical and biological aspects of the MPA N-BB I (García
Alonso et al., 2018; Matano et al., 2019). Although we were aware of it,
we decided to characterize a food web representing the whole MPA N-BB I
year round since this is the first study of its type in the area.

These are the perspectives that we suggest should be considered to
improve our knowledge regarding the structure, functioning and stability
of the MPA N-BB:

Incorporate habitat heterogeneity, since the benthic community in the BB
and deep flanks differs {[}; Schejter \& Albano (2021){]}. This
heterogeneity might lead to distinct food web properties, hence
differences in ecosystem functioning and response to anthropogenic and
environmental perturbations (Cordone et al., 2020; Kortsch et al.,
2019). El caso de las ascidias (Tatián)

>>>>

      \affiliation[1]{Centro Austral de Investigaciones Cientificas
(CADIC-CONICET), Argentina}
    \affiliation[2]{Instituto Antartico Argentino (IAA), Argentina}
    \affiliation[3]{Instituto de Ciencias Polares, Ambiente y Recursos
Naturales (ICPA), Universidad de Tierra del Fuego (UNTDF), Argentina}
    \affiliation[4]{Instituto de Investigaciones Marinas y Costeras
(IIMYC), Universidad Nacional de Mar del Plata-CONICET, Argentina}
    \affiliation[5]{Wildlife Conservation Society, Argentina}
    \affiliation[6]{Instituto de Biodiversidad y Biologia Experimental y
Aplicada (IBBEA), Universidad de Buenos Aires-CONICET, Argentina}
    \affiliation[7]{Museo Argentino de Ciencias Naturales ``Bernardino
Rivadavia'', Argentina}
    \affiliation[8]{Instituto de Diversidad y Ecologia Animal
(IDEA-CONICET)}
    \affiliation[9]{Facultad de Ciencias Exactas, Fisicas y Naturales,
Universidad Nacional de Cordoba (UNC), Argentina}
    \cortext[cor1]{Corresponding author}

  \begin{abstract}
  Globally, the total area of the world ocean designated under marine
  protection has increased in the recent decades. The majority of these
  Marine Protected Areas (MPAs) focus on the presence of particularly
  vulnerable, keystone, or charismatic species, large numbers of endemic
  species, and/or high biodiversity across taxonomic levels. In the
  sub-Antarctic region, the level of ocean protection is mainly
  associated to oceanic islands, except for the MPAs Namuncurá - Banco
  Burdwood I and II (MPA N-BB, 53º--55ºS and 56º--62ºW, respectively),
  which are associated to a submarine plateau and its southern adjacent
  deep slope region, respectively. Here, we present the first detailed
  analysis of the network of predator-prey interactions (food web) for
  the MPA N-BB ecosystem. We applied a network approach to characterise
  the food web in terms of complexity and structure, and identifying the
  species' role in such a framework. In terms of complexity, the MPA
  N-BB food web consisted of 1780 predator-prey interactions and 375
  species, with a link density of 4.75 and a connectance of 0.01. In
  terms of structure, almost half of the consumers were omnivores
  (0.48), and the network displayed a small-world pattern. These
  findings suggest that the ecosystem might be vulnerable to external
  perturbations targeting highly connected species, although structural
  properties might provide resilience and resistance, resulting in a
  rearranged structure that preserves its original functions.
  Furthermore, we identified several species as important in terms of
  different aspects of trophic structure and functioning, and response
  to perturbations. We suggest that generalist species, mainly fishes,
  play a crucial role in the ecosystem's bentho-pelagic coupling process
  and that other species, besides the longtail southern cod
  \emph{Patagonotothen ramsayi} and the Fueguian sprat \emph{Sprattus
  fuegensis}, should be considered as relevant energy transfers for the
  ecosystem. Finally, we argue that the diversity of species, including
  both the benthic and pelagic habitats, is responsible for seccuring
  the connectivity within the food web against perturbations, therefore
  contributing to the structure and stability of the ecosystem.
  \end{abstract}
    \begin{keyword}
    Food web \sep Complexity \sep Structure \sep Marine Protected
Area \sep 
    Southwest Atlantic
  \end{keyword}

@@

High-latitude marine ecosystems, such as the MPA N-BB, are considered
complex systems in terms of biodiversity and ecological interactions
(Cordone et al., 2020; Day et al., 2013; Kortsch et al., 2019; Trathan
et al., 2021). Although there is a robust knowledge about the complexity
considering the richness of the benthic and plankton communities in the
MPA N-BB ecosystem (APN, 2022; Guinder et al., 2020; Schejter et al.,
2016, 2020), a better understanding of species interactions' complexity
and structure is needed. This aspect can be tackled by analysing one of
the most frequent relationships between species: the predator-prey
interaction (Bascompte, 2009). The sum of predator-prey or trophic
interactions of a particular region is referred to as a food web,
representing the roadmap for matter and energy flow in an ecosystem. In
recent years, network approaches have been successfully applied to study
complex high-latitude marine ecosystems, improving our knowledge on
structure, functioning, and response to environmental/anthropogenic
changes (Cordone et al., 2018; Funes et al., 2022; Kortsch et al., 2015;
Marina et al., 2023). Among anthropogenic threats, it is worth
mentioning that contaminants like mercury and microplastics have been
recently reported as important threats to the MPA N-BB region (Cossi et
al., 2021; Di Mauro et al., 2022; Fioramonti et al., 2022).

In the present work, we present the first detailed analysis of the
network of predator-prey interactions, hereafter food web, for the MPA
N-BB ecosystem. For this, we applied a network approach to a highly
resolved food web. The objective was twofold: characterise the food web
in terms of complexity and structure, and identify the species' role in
such a network framework.

@@

We analysed the MPA N-BB network of trophic interactions, or food web,
at two levels: A) network, considering species and interactions of the
whole network; and B) species, considering interactions and species
related to a particular species (Table 1).

The network-level analysis aims to characterise the food web in terms of
complexity and structure. For this, we calculated several network
properties commonly used to describe empirical food webs (Pascual \&
Dunne, 2005): (1) number of species S; (2) number of interactions or
links L; (3) link density L/S; (4) connectance L/S\^{}2; (5) omnivory
Omn; and (6) small-world pattern. In order to explore the small-world
phenomenon, we analysed the characteristic path length (CPL) and the
clustering coefficient (CC). The CPL is the average shortest path length
between all pairs of nodes (Watts \& Strogatz, 1998). Here, CPL was
calculated as the average number of nodes in the shortest path
\(CPL_{Min} (i,j)\) between all pairs of nodes \(S(i,j)\) in a network
averaged over \(S(S-1)/2\) nodes:

@@

In terms of complexity, the MPA Namuncurá - Banco Burdwood food web
(N-BB I and II) consisted of 1780 predator-prey interactions and 375
species, where 93\% of them were defined at the species taxonomical
level (Figure 2, Table S2). The food web presented a link density (e.g.,
the average number of interactions per species) of 4.75, and a
connectance of 0.01. Almost half of the consumers were omnivores (0.48),
feeding on sources at different trophic levels. The food web displayed a
small-world pattern, meaning that the path length was lower and the
clustering coefficient higher than the random networks (Table 2).

@@

\caption{\label{tab:table2}Network-level properties of the MPA Namuncurá - Banco Burdwood food web. CPL: Characteristic Path Length; CC: Clustering Coefficient; SW: Small-World pattern. See table 1 for definitions and ecological relevance.}
\centering
\begin{tabular}[t]{r|r|r|r|r|r|r|l}
\hline
\textbf{Species} & \textbf{Interactions} & \textbf{Density} & \textbf{Connectance} & \textbf{Omnivory} & \textbf{CPL} & \textbf{CC} & \textbf{SW}\\
\hline
375 & 1780 & 4.75 & 0.01 & 0.48 & 2.96 & 0.08 & True\\
\hline
\end{tabular}
\end{table}

The degree distribution of the food web showed an asymmetric frequency
in the number of interactions, where most of the species had a
relatively low number of interactions and few species concentrated most
of them (Figure 3A). The distribution of prey among predators showed
that most consumers fed on a low number of prey whereas few had multiple
prey (Figure 3B). The top-five predators in number of prey were:
yellowfin notothen \emph{Patagonotothen guntheri} (Notothenioid fish, 50
prey), rock cod \emph{Patagonotothen ramsayi} (Notothenioid fish, 49
prey), broad nose skate \emph{Bathyraja brachyurops} (Chondrichthyan, 33
prey), Patagonian toothfish \emph{Dissostichus eleginoides}
(Notothenioid fish, 30 prey), and graytail skate \emph{Bathyraja
griseocauda} (Chondrichthyan, 28 prey). Following the same distribution
pattern, few prey presented multiple predators (Figure 3C). The top-five
prey in number of predators were: Detritus (Non-living, 155 predators),
the three categories of Diatoms considered (benthic, centric and
pennate, 75 predators on average), and species of the genus
\emph{Euphausia} (Zooplankton, 47 predators). Finally, taking into
account the interactions within each functional group, most interactions
were concentrated in a few species (Figure 3D). The most evident species
were: \emph{Doryteuthis gahi} (Cephalopoda), \emph{Grimothea gregaria}
(Decapoda), \emph{Patagonotothen ramsayi}, \emph{Patagonotothen
guntheri} and \emph{Dissostichus eleginoides} (bentho-pelagic fish),
\emph{Sprattus fuegensis} and \emph{Micromesistius australis} (pelagic
fish), and species of \emph{Euphausia} and \emph{Themisto gaudichaudii}
(Zooplankton). Overall, there is an evident asymmetry in the
distribution of interactions among species at different levels in the
MPA N-BB food web.

@@

\caption{Degree distributions for the (A) food web, for (B) prey among predators, (C) predators among prey, and (D) for each functional group. Groups are vertically ordered by increasing trophic level (following coloration of figure 2); groups with less than 3 species were not plotted (e.g., pelagic fish). All functional groups and the species that comprise them are shown in Supplementary Material (Table S3).}\label{fig:figure3}
\end{figure}

@@

We found different relationships between the species trophic level (TL)
and the rest of the analysed species-level properties (Figure 4A-D). The
most evident significant relationship was with trophic similarity,
i.e.~the higher the species' TL, the lower the trophic similarity or the
higher the uniqueness in terms of trophic role (Figure 4C). Here it is
noteworthy to highlight those high-trophic level species (TL
\textgreater{} 3.1) with low values of trophic similarity:
\emph{Bathyraja macloviana} and \emph{Squalus acanthias}
(Chondrichthyans), \emph{Diplopteraster clarki} and \emph{Pteraster sp}
(echinoderms), \emph{Phalacrocorax atriceps} and \emph{Eudyptes
chrysocome} (seabirds), and \emph{Lagenorhynchus cruciger} (marine
mammals) (Table S3).

We also found a significant negative relationship between TL and
closeness, however less evident, meaning that low-TL species are
relatively closer to any other species in the food web (Figure 4B).
Detritus, species of genera \emph{Calanus} and \emph{Euphausia}, and
Foraminifera, all with TL \textless{} 3, registered the highest
closeness values (Table S3).

Notably, species of mid-TLs (3-4.2) showed the highest values of
betweenness, meaning that those species participated in the highest
number of shortest paths between species (Figure 4A). The following are
the species with the highest values: \emph{Patagonotothen ramsayi},
\emph{Salilota australis}, \emph{Dissostichus eleginoides} (fishes),
\emph{Doryteuthis gahi} (Cephalopoda), and \emph{Patagonotothen
guntheri} (Notothenioid fish) (Table S3).

Considering the topological role, `module specialist' species were the
most frequent and presented a wide TL range (1 - 4.7), as well as
`module hub' species (TL = 1 - 4); `module connector' was constrained to
mid-TLs (2 - 3.86); and `network connector', the least frequent, had all
of its species in low-TLs (1 - 2), except for one with TL = 3.48 (Figure
4D, see Figure S2 for species' topological roles in a food web graph
framework). Here it is important to highlight the two latter topological
roles because they are responsible for linking modules and maintaining
the connectivity of the food web: 41 species (4 network connectors + 37
module connectors) from 19 different functional groups with a TL range =
1 - 3.86. The following were the four species with a network connector
role: detritus, benthic diatoms, Foraminifera and \emph{Patagonotothen
ramsayi}. The 37 species with a module connector role represented these
functional groups: Amphipoda, Bivalvia, Brachiopoda, Bryozoa, Hydrozoa
(as `Cnidaria\_benthic'), Copepoda, Cumacea, Decapoda, diatoms,
Echinodermata, fish (bentho-pelagic and demersal Osteichthyes, and
Chondrychthyes), Polychaeta, Porifera, Pycnogonida (as `Benthos\_Misc')
and zooplankton (see Supplementary Material Table S3 for the identity of
the species).

@@

\caption{Species-level properties by trophic level: (A) betweenness, (B) closeness, (C) trophic similarity, and (D) topological role. Each point represents a species. Linear regressions for betweenness ($y = 74.96x - 121.71, R^2 = 0.05, p-value < 0.01$), closeness ($y = 1.01e-05x - 9.48e-4, R^2 = 0.003, p-value = 0.14$) and trophic similarity ($y = -0.02x + 0.11 , R^2 = 0.08, p-value < 0.01$). Note that for panels A, B and C only species with TLs equal or greater than 2 were considered.}\label{fig:figure4}
\end{figure}

@@

It is suggested that the small-world pattern, i.e., a network with short
path length and high clustering coefficient, is not frequent in complex
marine food webs, mainly due to a low clustering coefficient compared to
random networks (Dunne et al., 2002c; Marina, Saravia, et al., 2018).
However, the food web of the MPA N-BB does display a small-world
pattern. Consequences of this could be of great importance in
recognizing evolutionary paths and the vulnerability to perturbations
(Montoya \& Solé, 2002). On the one hand, a short path length implies a
rapid spread of an impact (e.g., contaminant, population fluctuation,
local extinction) throughout the network but, at the same time, more
potentially adaptive dynamics in the face of external perturbations
(Montoya \& Solé, 2002; Williams et al., 2002). On the other hand, a
high clustering coefficient indicates the formation of subnetworks
composed only by the neighbours of particular species. This translates
into a greater resistance of the network due to the confinement of
perturbations mainly within subnetworks and not spreading between them
(Heer et al., 2020; Kortsch et al., 2019). Overall, a small-world
topology provides ecological networks with greater resilience and
resistance (Bornatowski et al., 2017; Dormann et al., 2017).

@@

We have identified that most of the consumers in the food web of the MPA
N-BB either have a narrow diet or are specialists, while few present a
broad diet. The most evident generalist species are \emph{Patagonotothen
guntheri} (Covatti Ale et al., 2022), \emph{P. ramsayi} (Fischer et al.,
2022), \emph{Dissostichus eleginoides} (Troccoli et al., 2020),
\emph{Bathyraja brachyurops} (Belleggia et al., 2008), and \emph{B.
griseocauda} (Bellegia et al., 2014), with more than 25 potential prey.
Since these species present mid-trophic positions in the food web (3-4),
acting as predator and prey, they might be important links between lower
and higher trophic levels. This result is in agreement with the sole
analysis, using stable isotopes, that exists so far for the trophic
structure of the MPA N-BB (Riccialdelli et al., 2020), and resembles
other high-latitude marine systems of the Southwest Atlantic and
Antarctic regions (Arkhipkin \& Laptikhovsky, 2013; Marina, Salinas, et
al., 2018). The importance of these particular generalist species also
arises since they feed on the benthic and pelagic habitats (Covatti Ale
et al., 2022; Fischer et al., 2022; Troccoli et al., 2020), linking
these realms and contributing to the vertical carbon flow.

On the other hand, a low number of prey are consumed by many predators
in the food web of the MPA N-BB. This suggests that there are dominant
food sources from which most consumers depend on and from where the
ecosystem energy is being transferred to the upper trophic levels. The
most demanded source we identified in this study (i.e.~detritus)
supports the abundant benthic community of filter-feeders (Schejter et
al., 2016). Furthermore, we found that the second and third-most
consumed prey were diatoms and species of \emph{Euphausia},
respectively, which are essential sources for the diverse zooplankton
community (Spinelli et al., 2020), mid-TL consumers like the Fuegian
sprat \emph{Sprattus fuegensis} (Padovani et al., 2021) and
\emph{Patagonotothen ramsayi} (Fischer et al., 2022), and top predators
such as the black-browed and grey-headed albatrosses (\emph{Thalassarche
melanophris} and \emph{Thalassarche chrysostoma}, respectively) (Catry
et al., 2004), and baleen whales (species of the genera Balaenoptera and
Eubalaena) (Valenzuela et al., 2018).

@@

Ecosystems with a pronounced `wasp-waist' structure are suggested to
present a high trophic redundancy, since many species would show similar
trophic habits (Cury et al., 2000). The significant negative
relationship between trophic similarity and trophic level enhances the
hypothesis of functional similarity at low and mid-TL species compared
to higher TL species for the MPA N-BB food web (Riccialdelli et al.,
2020). At the same time, our results highlight the uniqueness in terms
of the trophic role of high-TL predators. Here, not only the expected
pelagic animals such as marine mammals and seabirds arise as relevant,
but also benthic vertebrate (chondrichthyans \emph{Bathyraja macloviana}
and \emph{Squalus acanthias}) and invertebrate species (echinoderms
\emph{Diplopteraster clarki} and \emph{Pteraster sp}) are noteworthy.
The role that such species play in the MPA N-BB ecosystem is unique and
perturbations on them might result in unprecedented changes at the
trophic structure and functioning level.

@@

The food web studied in the present work might be more representative of
the MPA Namuncurá - Banco Burdwood I ecosystem, which comprises the
shallow submarine plateau called Burdwood Bank. This is related to the
sampling effort that was conducted during the research cruises in the
former MPA compared to the MPA N-BB II (i.e.~deep flanks to the south).
As a consequence, most of the data we used to build the network come
from studies performed in the MPA N-BB I. Despite this fact, we decided
to build the food web considering both MPAs due to the tight
oceanographic and ecological connection that exists among them (APN,
2022 and references therein).

@@

The MPA N-BB I presents complex oceanographic conditions that generate
an internal spatial heterogeneity, mainly along its longitudinal axis
(Matano et al., 2019). Up to date this heterogeneity has been reflected
in phytoplankton and zooplankton communities (Bértola et al., 2018;
García Alonso et al., 2020; Spinelli et al., 2020), and in fish
assemblages (Delpiani et al., 2020). Moreover, seasonal variations also
occur in some physical and biological aspects of the MPA N-BB I (García
Alonso et al., 2018; Matano et al., 2019). Considering both MPAs (N-BB I
and II), a seasonal variation in the community composition of marine
mammals and seabirds was recorded recently (Dellabianca et al., 2023).
The spatial and seasonal variations in the plankton community might
affect the energy and matter flow to higher levels of the food web. This
has been recently studied in the vicinity of the MPA N-BB I, in the
Beagle Channel, where a differential energy flow pattern of the plankton
community has been recognised in two micro-basins of the Channel
separated by a sill, each with different physicochemical properties
(Giesecke et al., 2021), nutrient concentration (Latorre et al., 2023)
as well as in the dominant component of the plankton community (Bruno et
al., 2023; Presta et al., 2023). Although we were aware of the above, we
decided to characterise a food web representing the whole MPA N-BB I
year round since this is the first study of its type in the area.
